Manuscript draft

### 2019-06-14 manuscript/manuscript draft.Rmd
Update manuscript draft.Rmd
updated manuscript draft

@@

Data that control for stand age and standardize methodologies are required to resolve this question. Here, we use a comprehensive global database to explore global patterns in productivity. We explore three questions: 
1. **Which climatic variables are the most important drivers behind the latitudinal pattern in primary productivity?** To date, the majority of studies have focussed on productivity responses to precipitation and temperature, while the influence of other climate variables on productivity remains under-explored. We utilise global climate datasets to investigate the relationships between productivity and a range of climate variables.  
2. **Do the components of primary productivity show variation in their responses to these climatic drivers?** Allocation to components of primary productivity appears to show some variation across climate and latitudinal gradients. We use global datasets of a range of primary productivity components to explore how significant this variation in allocation is.  
3. **Does climate explain the same proportion of variation in different components of primary productivity?** Review of current research shows that, while the relationship between GPP and latitude is consistent, NPP and ANPP show weaker relationships with latitude. This may be a result of varying sensitivities to climate drivers. We use mixed models to estimate the proportion of variation explained by climate for different components of productivity, to investigate how the relative importance of climatic drivers varies across components.

@@

###References

>>>>

###Abstract

Globally, forests are a significant carbon sink, showing high levels of productivity and representing an important component of the carbon cycle. Current knowledge indicates that forest productivity decreases with latitude; however, there is evidence that this relationship varies across different fluxes. Furthermore, the climate variables that drive this relationship are poorly understood. Here, we use a comprehensive global database of forest carbon fluxes to show that, while all major carbon fluxes decrease with latitude, allocation to woody productivity increases with latitude, and allocation to root productivity declines. The best predictors of global patterns of productivity are temperature variables, including mean annual temperature, annual temperature range, and temperature seasonality, with the exception of woody productivity, which is most strongly influenced by potential evapotranspiration and vapour pressure deficit. Climate variables explain a large proportion of the variation in major carbon fluxes, but are a less significant predictor of subsidiary components. Our results illustrate the strong influence of climate on primary productivity, and particularly the importance of temperature in determining forest productivity. However, they also indicate that effects of climate are complex: fluxes show non-linear responses to climate variables, and many factors other than climate interact to determine allocation to subsidiary components. Knowledge of the relative influence of climate variables on forest carbon fluxes is an important component of understanding the responses of primary productivity to climate change.

@@

Data that control for stand age and standardize methodologies are required to resolve this question. Here, we use a comprehensive global database of forest carbon fluxes to explore global patterns in productivity. We explore three questions: 
1. **Which climatic variables are the most important drivers behind the latitudinal pattern in primary productivity?** To date, the majority of studies have focussed on productivity responses to precipitation and temperature, while the influence of other climate variables on productivity remains under-explored. We utilise global climate datasets to investigate the relationships between productivity and a range of climate variables.  
2. **Do the components of primary productivity show variation in their responses to these climatic drivers?** Allocation to components of primary productivity appears to show some variation across climate and latitudinal gradients. We use global datasets of a range of primary productivity components to explore how significant this variation in allocation is.  
3. **Does climate explain the same proportion of variation in different components of primary productivity?** Review of current research shows that, while the relationship between GPP and latitude is consistent, NPP and ANPP show weaker relationships with latitude. This may be a result of varying sensitivities to climate drivers. We use mixed models to estimate the proportion of variation explained by climate for different components of productivity, to investigate how the relative importance of climatic drivers varies across components.

@@

*Does climate explain the same proportion of variation in different components of primary productivity?*
